---
title: "Effect of Democratization on Deforestation"
output:
  pdf_document: default
  html_document: default
---
### Students: Albert Yao and Takeo Tokunari

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(knitr)
library(modelsummary)
```


1. Effect of democratization on deforestation (all countries)
```{r demo vs for, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

di <- read_excel("Democracy-Index-2019.xlsx") %>%
  rename("Country" = `2019`) %>% 
  rename("2019" = `...4`) %>%
  select(c("Country", "2019", "2015", "2010"))

forest <- read_excel("Forest Area.xlsx", sheet = 2) %>%
  select(c("Country and Area", "Forest Area, 2010", "Forest Area, 2015", "Forest Area, 2020")) %>% 
  rename("Country" = "Country and Area") 

for_change <- forest %>%
  group_by(Country) %>%
  summarize(change2015 = (`Forest Area, 2015` - `Forest Area, 2010`)/`Forest Area, 2010`, 
            change2020 = (`Forest Area, 2020` - `Forest Area, 2015`)/`Forest Area, 2015`)

di_forest <- di %>% 
  right_join(for_change)

df2015 <- di_forest %>% 
  select(Country, `2015`, change2015)
df2015_lm <- lm(change2015 ~ `2015`, data = df2015)

df2015 %>% 
  ggplot(aes(x = `2015`, y = change2015, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.02, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(breaks = c(0:10), labels = c(0:10), limits = c(0, 10)) +
  labs(
    title = "Democracization's Effect on Deforestation, 2015",
    x = "Democracy Index",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

coefs <- c(
  "(Intercept)" = "Intercept",
  "`2015`" = "Democracy Index in 2015",
)
modelsummary::modelsummary(df2015_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

```

2. Effect of democratization on deforestation (countries with forest)
```{r big country, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

for_big <- forest %>% 
  filter(`Forest Area, 2010` >= 1000) %>% 
  group_by(Country) %>%
  summarize(change2015_big = (`Forest Area, 2015` - `Forest Area, 2010`)/`Forest Area, 2010`)
di_forest_big <- di %>% 
  right_join(for_big)

df2015_big <- di_forest_big %>% 
  select(Country, `2015`, change2015_big)
df2015_big_lm <- lm(change2015_big ~ `2015`, data = df2015_big)

df2015_big %>% 
  ggplot(aes(x = `2015`, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.01, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(breaks = c(0:10), labels = c(0:10), limits = c(0, 10)) +
  labs(
    title = "Democracization's Effect on Deforestation, 2015",
    subtitle = "Countries with forest land over one million hectares",
    x = "Democracy Index",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

coefs <- c(
  "(Intercept)" = "Intercept",
  "`2015`" = "Democracy Index in 2015"
)

modelsummary::modelsummary(df2015_big_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

```

3. Agricultural land growth (countries with forest)
```{r agri, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

agri <- read_csv("WB_Agri_Land_Cleaned.csv") %>% 
  group_by(`Country Name`) %>%
  summarize(agri_change = (Agri_2015 - Agri_2011)/Agri_2011) %>% 
  rename("Country" = `Country Name`) %>% 
  right_join(for_big)
agri_lm <- lm(change2015_big ~ agri_change, data = agri)

agri %>% 
  ggplot(aes(x = agri_change, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.005, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Agricultural Land Growth and Deforestation, 2015",
    x = "Agricultural Land Growth",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

coefs <- c(
  "(Intercept)" = "Intercept",
  "agri_change" = "Change in agricultural land"
)

modelsummary::modelsummary(agri_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

```


4. GDP per capita growth (countries with forest)
```{r gdp, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

gdp <- read_csv("WB_GDPperCapita_Cleaned.csv", 
    col_types = cols(GDPcap_2015 = col_double())) %>%
#    filter(GDPcap_2015 < 20000) %>% 
    select(`Country Name`, `Country Code`, `GDPcap_2015`) %>% 
    rename("Country" = "Country Name") %>% 
    right_join(for_big) 
gdp_lm <- lm(change2015_big ~ GDPcap_2015, data = gdp)
coefs <- c(
  "(Intercept)" = "Intercept",
  "GDPcap_2015" = "GDP per capita in 2015"
)

modelsummary::modelsummary(gdp_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

gdp %>% 
  ggplot(aes(x = GDPcap_2015, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.005, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "GDP Per Capita and Deforestation, 2015",
    x = "GDP Per Capita",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

```
5. GDP per capita (countries with forest and with less than US$20,000 GDP per capita)
```{r}
gdp_less_20000 <- read_csv("WB_GDPperCapita_Cleaned.csv", 
    col_types = cols(GDPcap_2015 = col_double())) %>%
    filter(GDPcap_2015 < 20000) %>% 
    select(`Country Name`, `Country Code`, `GDPcap_2015`) %>% 
    rename("Country" = "Country Name") %>% 
    right_join(for_big) 
gdp_less_20000_lm <- lm(change2015_big ~ GDPcap_2015, data = gdp_less_20000)
coefs <- c(
  "(Intercept)" = "Intercept",
  "GDPcap_2015" = "GDP per capita in 2015"
)
modelsummary::modelsummary(gdp_less_20000_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

gdp_less_20000 %>% 
  ggplot(aes(x = GDPcap_2015, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.005, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "GDP Per Capita and Deforestation, 2015",
    x = "GDP Per Capita",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()


```


6. GDP growth per capita (countries with forest)
```{r gdp growth, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

gdp_growth <- read_csv("WB_GDP_Growth_per_Capita_Cleaned.csv") %>% 
  select(`Country Name`, `Country Code`, `GrowthCap_2015`) %>% 
  rename("Country" = "Country Name") %>% 
  right_join(for_big) %>% 
  filter(Country != "Sierra Leone")
gdp_growth_lm <- lm(change2015_big ~ GrowthCap_2015, data = gdp_growth)

gdp_growth %>% 
  ggplot(aes(x = GrowthCap_2015, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.005, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "GDP Growth Per Capita and Deforestation, 2015",
    x = "GDP Growth Per Capita",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

coefs <- c(
  "(Intercept)" = "Intercept",
  "GrowthCap_2015" = "GDP growth per capita in 2015"
)
modelsummary::modelsummary(gdp_growth_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)
```


7. Poverty ratio (countries with forest)
```{r pov, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

pov_ratio <- read_csv("World_Bank_Poor_Ratio_Cleaned.csv") %>% 
#  filter(`Average_2011-2015` > 5) %>% 
  rename("Country" = `Country Name`) %>% 
  select(Country, `Average_2011-2015`) %>% 
  right_join(for_big)

pov_ratio %>% 
  ggplot(aes(x = `Average_2011-2015`, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.01, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Poverty Ratio and Deforestation, 2015",
    x = "Poverty Ratio",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

pov_lm <- lm(change2015_big ~ `Average_2011-2015`, data = pov_ratio)
coefs <- c(
  "(Intercept)" = "Intercept",
  "`Average_2011-2015`" = "Poverty ratio (2011-2015 average)"
)
modelsummary::modelsummary(pov_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

```

8. Poverty ratio (countries with forest and poverty ratio of 5% or higher)
```{r pov5, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

pov_ratio_5 <- read_csv("World_Bank_Poor_Ratio_Cleaned.csv") %>% 
  filter(`Average_2011-2015` > 5) %>% 
  rename("Country" = `Country Name`) %>% 
  select(Country, `Average_2011-2015`) %>% 
  right_join(for_big)

pov_ratio_5 %>% 
  ggplot(aes(x = `Average_2011-2015`, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.01, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Poverty Ratio and Deforestation, 2015",
    x = "Poverty Ratio",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

pov_lm_5 <- lm(change2015_big ~ `Average_2011-2015`, data = pov_ratio_5)
coefs <- c(
  "(Intercept)" = "Intercept",
  "`Average_2011-2015`" = "Poverty ratio (2011-2015 average)"
)
modelsummary::modelsummary(pov_lm_5, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

```
9. Gini Index (countries with forest)
```{r gini, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

gini <- read_csv("WB_Gini_Cleaned.csv") %>%
  select(`Country Name`, `Country Code`, Gini_2015) %>% 
  slice(1:169) %>% 
  rename("Country" = "Country Name") %>% 
  right_join(for_big) 

gini_lm <- lm(change2015_big ~ Gini_2015, data = gini)

gini %>% 
  ggplot(aes(x = Gini_2015, y = change2015_big, label = Country)) +
  geom_point() +
  geom_text(vjust = 0, nudge_y = 0.005, size = 3) + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "Gini Index and Deforestation, 2015",
    x = "Gini Index",
    y = "Change in Forest Area from 2010 to 2015"
  ) +
  theme_bw()

coefs <- c(
  "(Intercept)" = "Intercept",
  "Gini_2015" = "Gini Index in 2015"
)
modelsummary::modelsummary(gini_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

```

10. Does Gini Index explain the difference in the effect of democratization on deforestation?

Model 1: average treatment effect of Gini Index as a binary variable
```{r hypo test, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

gini_avg <- read_csv("WB_Gini_Cleaned_1.csv") %>% 
  select(`Country Name`, `Country Code`, `Gini_2011-2015`) %>% 
  slice(1:169) %>% 
  filter(!is.na(`Gini_2011-2015`)) 

gini_avg_best <- gini_avg %>% 
  arrange(`Gini_2011-2015`) %>% 
  slice(1:30) %>% 
  mutate(gap = 1)

gini_avg_worst <- gini_avg %>% 
  arrange(desc(`Gini_2011-2015`)) %>% 
  slice(1:30) %>% 
  mutate(gap = 0)
  
gini_bw <- gini_avg_best %>% 
  rbind(gini_avg_worst) %>% 
  rename("Country" = "Country Name") %>% 
  right_join(for_big) %>% 
  filter(!is.na(change2015_big)) %>% 
  filter(!is.na(gap)) %>% 
  group_by(gap) %>%
  summarize(
    for_mean = mean(change2015_big),
    for_se = sd(change2015_big)/sqrt(n())
  )  %>% 
  pivot_wider(names_from = gap, values_from = c(for_mean, for_se)) %>% 
  mutate(
    for_diff = for_mean_1 - for_mean_0,
    for_diff_se = sqrt(for_se_1 ^ 2 + for_se_0 ^ 2),
    ci_lower = for_diff - 1.96 * for_diff_se,
    ci_upper = for_diff + 1.96 * for_diff_se
  )
for_diff_z <- (gini_bw$for_diff - 0)/gini_bw$for_diff_se
for_diff_p <- 2 * pnorm(abs(for_diff_z))
  
```


Model 2: multivariable linear regression
```{r combine lm, echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}

all_data <- di_forest %>% 
  left_join(gini) %>% 
  left_join(gdp_growth) %>% 
  left_join(gdp) %>% 
  left_join(pov_ratio) %>% 
  filter(!is.na(Gini_2015)) %>% 
  filter(!is.na(GrowthCap_2015)) %>% 
  filter(!is.na(GDPcap_2015)) %>% 
  filter(!is.na(`Average_2011-2015`)) %>% 
  rename("Democracy.Index.in.2015" = `2015`) %>% 
  rename("Gini.Index.in.2015" = `Gini_2015`) %>% 
  select(!`2019`)

all_lm <- lm(change2015 ~ Democracy.Index.in.2015 + Gini.Index.in.2015 + Gini.Index.in.2015 * Democracy.Index.in.2015, data = all_data)

# I do not seem to understand how to show the interaction term
coefs <- c(
  "(Intercept)" = "Intercept",
  "`2015`" = "Democracy Index in 2015",
  "Gini_2015" = "Gini Index in 2015",
  "`2015` × Gini_2015" = "test"
)
#modelsummary::modelsummary(all_lm, coef_map = coefs, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)

modelsummary::modelsummary(all_lm, gof_omit = "AIC|BIC|Log.Lik.|F", stars = TRUE)
```
## Code
```{r print-code, ref.label=knitr::all_labels(), echo = TRUE, eval=FALSE} 

```

